Generative Adversarial Networks

### 2017-12-06 cs6735/assignment/report.tex
few changes

\section{Objectives}
\begin{enumerate}
  \item Implement the following machine learning algorithms:
  \begin{enumerate}
    \item ID3
    \item Adaboost on ID3
    \item Random Forest
    \item Naïve Bayes
    \item Adaboost on Naïve Bayes
    \item K-nearest neighbors
  \end{enumerate}
  \item Evaluate the algorithms on the following datasets:
  \begin{enumerate}
    \item Brest Cancer Data
    \item Car Data
    \item Ecoli Data
    \item Mushroom Data
  \end{enumerate}
  \item Create report of the experimental study including:
  \begin{enumerate}
    \item Description of the learning algorithms you implement.
    \item Description of the datasets you use (number of examples, number of attribute, number of classes, type of attributes, etc.).
    \item Technical details of your implementation: pre-processing of data sets (discretization, etc.), parameter setting, etc.
    \item Design of your programming implementation (data structures, overall program structure).
    \item Report and analysis of your experimental results using using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
    \item Comparison and discussion of the algorithms with respect to the experimental results.
  \end{enumerate}
\end{enumerate}

@@

\subsection{Adaboost} \label{adaboost}
Adaboost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire. This type of ensemble learning uses a set of weak learners to reduce bias and become a strong learner. It solves many of the difficulties associated with previous boosting algorithms \cite{Schapire:1999:BIB:1624312.1624417}.

The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$. This value increases when the sample is misclassified and decreases when the sample is correctly classified. The target values are assumed be to in the set ${+1, -1}$. The Adaboost algorithm is easily implemented on weak learners which are parameterized by sample weights. Neither Naïve Bayes or ID3 natively implement weighted training. Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights. For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.

@@

\subsubsection{Adaboost on Naïve Bayes}
Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes. This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the Adaboost algorithm.

\subsubsection{Adaboost on ID3}
The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion. Therefore, to implement Adaboost on ID3, the depth of the trees were limited to one level. This type of tree is known as a \ii{decision stump}.

@@

\subsection{Adaboost on Naïve Bayes}
number of learners

\subsection{Adaboost on ID3}
number of learenrs

@@

\subsection{dt}
This package contains all of the objects associated with decision trees.

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{Adaboost}:
  \item[] \bb{AdaboostModel}:
  \item[] \bb{Multi-Adaboost}:
  \item[] \bb{Multi-AdaboostModel}:
  \item[] \bb{RandomForest}:
  \item[] \bb{RandomForstModel}:
\end{enumerate}

@@

\subsection{nb}
This package contains all of the objects associated with Naïve Bayes.

@@

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    Adaboost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Adaboost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}

>>>>

\section{Objectives}
\begin{enumerate}
  \item Implement the following machine learning algorithms:
  \begin{enumerate}
    \item ID3
    \item AdaBoost on ID3
    \item Random Forest
    \item Naïve Bayes
    \item AdaBoost on Naïve Bayes
    \item K-nearest neighbors
  \end{enumerate}
  \item Evaluate the algorithms on the following datasets:
  \begin{enumerate}
    \item Brest Cancer Data
    \item Car Data
    \item Ecoli Data
    \item Mushroom Data
  \end{enumerate}
  \item Create report of the experimental study including:
  \begin{enumerate}
    \item Description of the learning algorithms you implement.
    \item Description of the datasets you use (number of examples, number of attribute, number of classes, type of attributes, etc.).
    \item Technical details of your implementation: pre-processing of data sets (discretization, etc.), parameter setting, etc.
    \item Design of your programming implementation (data structures, overall program structure).
    \item Report and analysis of your experimental results using using 10 times 5-fold cross-validation (include mean, standard deviation of accuracies).
    \item Comparison and discussion of the algorithms with respect to the experimental results.
  \end{enumerate}
\end{enumerate}

@@

\subsection{AdaBoost} \label{adaboost}
AdaBoost is a boosting algorithm that was first introduced in 1995 by Freunb Schapire. This type of ensemble learning uses a set of weak learners to reduce bias and become a strong learner. It solves many of the difficulties associated with previous boosting algorithms \cite{Schapire:1999:BIB:1624312.1624417}.

The primary part of the algorithm is to maintain a weight value $w$ for every sample within the data $S$. This value increases when the sample is misclassified and decreases when the sample is correctly classified. The target values are assumed be to in the set ${+1, -1}$. The AdaBoost algorithm is easily implemented on weak learners which are parameterized by sample weights. Neither Naïve Bayes or ID3 natively implement weighted training. Therefore, an alternative implementation was used where a subset of the training data is selected with replacement based on the weights. For example, if the weight vector for two samples is ${1, 2}$, the second sample is twice as likely to be picked each time.

@@

\subsubsection{AdaBoost on Naïve Bayes}
Naïve Bayes is an inherently weak learner due to its assumption of conditional independence amongst attributes. This fact introduces a large amount of preference bias which makes a Naïve Bayes and ideal candidate for the AdaBoost algorithm.

\subsubsection{AdaBoost on ID3}
The ID3 algorithm does not introduce a large amount of preference bias and often overfitting if allowed to train to completion. Therefore, to implement AdaBoost on ID3, the depth of the trees were limited to one level. This type of tree is known as a \ii{decision stump}.

@@

\subsection{AdaBoost on Naïve Bayes}
number of learners

\subsection{AdaBoost on ID3}
number of learners

@@

\subsection{tree}
This package contains all of the objects associated with decision trees.

@@

\begin{enumerate}[leftmargin=*]
  \item[] \bb{AdaBoost}:
  \item[] \bb{AdaBoostModel}:
  \item[] \bb{Multi-AdaBoost}:
  \item[] \bb{Multi-AdaBoostModel}:
  \item[] \bb{RandomForest}:
  \item[] \bb{RandomForstModel}:
\end{enumerate}

@@

\subsection{bayes}
This package contains all of the objects associated with Naïve Bayes.

@@

\section{Results}
\begin{table}
  \begin{tabular}{ |c|c|c|c|c|c| }
    \hline
    Breast Cancer           & Car      & Letter   & E. Coli  & Mushroom \\ \hline
    AdaBoost on ID3         & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    ID3                     & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Random Forest           & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    Naïve Bayes             & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    AdaBoost on Naïve Bayes & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
    K-Nearest Neighbor      & 100.00\% & 100.00\% & 100.00\% & 100.00\% \\ \hline
  \end{tabular}
  \caption{Results of the six implemented algorithms on five UCI Machine Learning repositories. Accuracy calculated using 10 times 5-fold cross validation.}
\end{table}
